On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-10-08 docs/mvfits_paper/mvf.tex
Fix minor typo in abstract

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %
  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
  %
  On important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
  %
  Here, we present new methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
  %
  In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
  %
  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon.
  %
  GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit.
  %
  GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
  %
  We discuss the use of these models in current and future gravitational wave signal modeling.
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  %
  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
  %
  One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
  %
  Here, we present new methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
  %
  In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
  %
  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon.
  %
  GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit.
  %
  GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
  %
  We discuss the use of these models in current and future gravitational wave signal modeling.
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
